FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions

### 2023-08-04 paper.tex
fix broken cite

We introduce \FlowFPX{}, a toolkit for debugging
\fp{} exceptions in an easy and intuitive way~(\cref{s:flowfpx}):
\begin{itemize}
  \item
    The centerpiece of \FlowFPX{} is \FT{}, a dynamic analysis tool that uses
    Julia's operator overloading to selectively monitor for exceptions and to
    fuzz code for vulnerabilities.
  \item
    To visualize results, \FT{} adapts coalesced stack-trace graphs 
    (CSTGs, or \CSTG{}s)~\cite{hmbdrg-cse-2014} for a whole-program view on the generation,
    propagation, and death of exceptional values.
  \item A companion tool \GPUFPX{}~\cite{llsflg-hpdc-2023} provides fine-grained insights for GPU kernels.
\end{itemize}
%
Together, the \FlowFPX{} tools have helped debug exceptions in a variety
of applications: from ocean simulations to heat models~(\cref{s:casestudies}).
That said, there is much more to explore.
\FlowFPX{} is a growing project and we welcome feedback from domain experts
on how to best suit their workflow.

>>>>

We introduce \FlowFPX{}, a toolkit for debugging
\fp{} exceptions in an easy and intuitive way~(\cref{s:flowfpx}):
\begin{itemize}
  \item
    The centerpiece of \FlowFPX{} is \FT{}, a dynamic analysis tool that uses
    Julia's operator overloading to selectively monitor for exceptions and to
    fuzz code for vulnerabilities.
  \item
    To visualize results, \FT{} adapts coalesced stack-trace graphs 
    (CSTGs, or \CSTG{}s)~\cite{humphreySystematicDebuggingMethods2014} for a whole-program view on the generation,
    propagation, and death of exceptional values.
  \item A companion tool \GPUFPX{}~\cite{llsflg-hpdc-2023} provides fine-grained insights for GPU kernels.
\end{itemize}
%
Together, the \FlowFPX{} tools have helped debug exceptions in a variety
of applications: from ocean simulations to heat models~(\cref{s:casestudies}).
That said, there is much more to explore.
\FlowFPX{} is a growing project and we welcome feedback from domain experts
on how to best suit their workflow.
